---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wordsalad

<!-- badges: start -->
[![R build status](https://github.com/EmilHvitfeldt/wordsalad/workflows/R-CMD-check/badge.svg)](https://github.com/EmilHvitfeldt/wordsalad/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of wordsalad is to provide a unified interface for word embedding methods to produce word vectors.

Goals of this package are:

- Allow the specification of tokenizer used
- Streamline argument names and order
- Consistant output formats

## Installation

If you want the development version instead then install directly from GitHub:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("EmilHvitfeldt/wordsalad")
```

## Example

```{r, message=FALSE}
library(wordsalad)

glove(fairy_tales)
```

## Code of Conduct
  
Please note that the wordsalad project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
